Wolfram Langauge interop with Wolframite

### 2024-01-28 docs/projects/math/wolframite/index.qmd
Wolframite - rerendered

This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
It is also appears at the Wolrfamite repo as [dev/kindly-demo.clj](https://github.com/scicloj/wolframite/blob/main/dev/kindly_demo.clj).
Note that to use Wolframite, you need Wolfamite in the dependencies,
as well as the `WOLFRAM_INSTALL_PATH`
set up in your system, as explained in
[Wolframite's README](https://github.com/scicloj/wolframite/).

@@

## Make sure Wo

@@

## Def // intern WL fns, i.e. effectively define WL fns as clojure fns:

>>>>

This notebook demonstrates basic usage of [Wolframite](https://github.com/scicloj/wolframite/) in a way that would work in visual tools supporting [Kindly](https://scicloj.github.io/kindly-noted/kindly).
It is also appears at the Wolrfamite repo as [dev/kindly-demo.clj](https://github.com/scicloj/wolframite/blob/main/dev/kindly_demo.clj).
Note that to use Wolframite, you need Wolfamite in the dependencies,
and if Wolfraimte fails to find the correct install path automatically,
you may need to have the `WOLFRAM_INSTALL_PATH` environment variable
set up in your system, as explained in
[Wolframite's README](https://github.com/scicloj/wolframite/).

@@

@@

## Def / intern WL fns, i.e. effectively define WL fns as clojure fns:
